Verifying Demonstrations

### 2018-05-25 paper/intro.tex

Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it is actually an adversarial setting. 
Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) have an incentive to decrease it.
In this case, we are left with two options: either we trust Alice or Grace (or 
another third party), or we have to be able to verify their claims ourselves.
In this paper, our main objective is to provide a scheme preventing both Alice and Grace from cheating (\ie their claim should be verifiable).
To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants'
privacy to the extent possible given their physical presence at the protest. 
More precisely, our solution will not be able to prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
Nonetheless, we can ensure that none of the digital traces generated by a participant in our scheme can be associated with their identity and that their actions are also unlinkable.
\sonja{what actions do we refer to here?}

\seb{to do complete the contributions}
\emph{Contributions.} In this paper, our main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
This verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.

@@

\emph{Limitations and assumptions.} Some of the assumptions that are required 
for implementing our proposition are not yet realized (briefly, use of smartphones, unique identities, distance bounding - see \cref{assumptions} 
for more detailed descriptions). In particular, not all (or even many) 
protesters, especially in countries with oppressive regimes, currently possess 
smartphones.
In addition, digital certificates signed by a central authority are not yet widely available and if we rely on government-issued credentials, we cannot prevent the government from performing Sybil attacks --- since it can issue arbitrarily many \emph{valid} credentials. 
\seb{maybe to prevent the above issue, we could require the individual to 
  generate his secret key and only use the authority to obtain a certification 
  on his public key (in the spirit of blind signature)}
\daniel{That's what we currently do.
  But the government is the authority, so the government can generate and 
  certify its own keys.}
In this case, it does not make sense to verify any pro-government protests in 
which Grace's authoritarian regime wants to demonstrate its wide support, 
\eg~\cite{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
Finally, achieving distance-bounding protocols on smartphones is currently not 
feasible within a meaningful range of distance needed for our scenario.
They lack the required hardware to do the distance bounding fast enough.

@@

\seb{to do, update the outline}
\daniel{done?}
\emph{Outline.} The paper is organized as follows. First, we define and 
formalize the notion of protest and discuss its relationship with electronic 
voting (\cref{SystemModel}).  We then present the desired security properties 
for such a system (\cref{Properties}) and subsequently discuss related work in 
terms of these properties (\cref{RelatedWork}). We give the relevant background 
on the building blocks of our solution, including our proposal for 
distance-bounding anonymous credentials that cope with a malicious 
(impersonating) verifier (\cref{BuildingBlocks}). \PRIVO, the protocol 
constructed from the building blocks, is presented next (\cref{Protocol}) and we 
analyze its security and privacy (\cref{SecurityAnalysis}) as well as 
performance and implementation issues (\cref{PerformanceAnalysis}). We conclude 
with a discussion.

>>>>

Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it is actually an adversarial setting. 
Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) have an incentive to decrease it.
In this case, we are left with two options: either we trust Alice or Grace (or 
another third party), or we have to be able to verify their claims ourselves.
In this paper, our main objective is to provide a scheme preventing both Alice and Grace from cheating (\ie their claim should be verifiable).
To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants'
privacy to the extent possible given their physical presence at the protest. 
More precisely, our solution will not be able to prevent an observer 
(physically present or looking at photos or videos) from recognizing a 
particular individual at a protest. Nonetheless, we can ensure that none of the 
digital traces generated by a participant in our scheme can be associated with 
their identity and that any witnessing is also unlinkable.

\emph{Contributions.} In this paper, our main contribution is to propose 
\PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd 
count in protests.
This verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.

@@

\emph{Limitations and assumptions.} Some of the assumptions that are required 
for implementing our proposition are not yet realized (briefly, use of smartphones, unique identities, distance bounding - see \cref{assumptions} 
for more detailed descriptions). In particular, not all (or even many) 
protesters, especially in countries with oppressive regimes, currently possess 
smartphones.
In addition, digital certificates signed by a central authority are not yet 
widely available and if we rely on government-issued credentials, we cannot 
prevent the government from performing Sybil attacks --- since it can issue 
arbitrarily many \emph{valid} credentials.
In this case, it does not make sense to verify any pro-government protests in 
which Grace's authoritarian regime wants to demonstrate its wide support, 
\eg~\cite{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
Finally, achieving distance-bounding protocols on smartphones is currently not 
feasible within a meaningful range of distance needed for our scenario.
They lack the required hardware to do the distance bounding fast enough.

@@

\emph{Outline.} The paper is organized as follows. First, we define and 
formalize the notion of protest and discuss its relationship with electronic 
voting (\cref{SystemModel}).  We then present the desired security properties 
for such a system (\cref{Properties}) and subsequently discuss related work in 
terms of these properties (\cref{RelatedWork}). We give the relevant background 
on the building blocks of our solution, including our proposal for 
distance-bounding anonymous credentials that cope with a malicious 
(impersonating) verifier (\cref{BuildingBlocks}). \PRIVO, the protocol 
constructed from the building blocks, is presented next (\cref{Protocol}) and 
we analyze its security and privacy (\cref{SecurityAnalysis}) as well as 
performance and implementation issues (\cref{PerformanceAnalysis}). We conclude 
with a discussion.
